\begin{cvblock}{Duties and Responsibilities}
\cvitem{2007--2015}{ Responsible Scientist for edge manipulators in RFX-mod
device}
\cvitem{2015-2016}{ Responsible Scientist Soft X ray diagnostic in the
  TCV tokamak. Deputy Responsible Scientist for the Neutral Beam
  Heating system in the TCV tokamak.}
\cvitem{2009}{Task force leader in RFX-mod experiment for task force
\emph{Particle, Momentum and energy transport}}
\cvitem{2010}{Task force leader in RFX-mod experiment for task force
\emph{Physics integration for high performance RFP}}
\cvitem{2011}{Coordinator of the EFDA working group \emph{3D field effects in
  edge and SOL and diagnostic development} under EFDA Transport
Topical Group.}
\cvitem{2012}{Member of the Program committee of the 17th Joint EU-US Transport Task Force
Meeting in combination with the 4th EFDA Transport Topical Group
meeting, 3-6 September 2012, Padova, Italy}
\cvitem{2013}{Scientific Coordinator of experiment \emph{B13-19
  Investigation of M-Mode} on JET Tokamak
campaigns C31-C34}
\cvitem{2014}{Scientific Coordinator of experiment \emph{AUG14-2.2-3, SOL
filamentary transport at high density}, under the MST1 Eurofusion
Work-Packages.}
\cvitem{2015-2016}{Scientific Coordinator of experiment
  \emph{TCV15-2.2-3: Filamentary Transport in the SOL} under MST1
  Eurofusion Work-Package.}
\cvitem{2015-2016}{Scientific Coordinator of experiment
  \emph{TCV15-1.5-1, Mitigation of high Z impurity accumulation
    through combined central ECRH and tailoring of MHD activity in
    high performance H-modes} under MST1 Eurofusion Work-Package.}
\cvitem{2017-2018}{Scientific Coordinator of Topic 21
  \emph{Filamentary transport in high-power H-mode conditions and in
    no/small-ELM regimes to predict heat and particle loads on PFCs
    for future devices }
  under MST1 Eurofusion Work-Package.}
\cvitem{2018-19}{Scientific Coordinator of JET Task T18-02 
  \emph{Scrape-off layer and SOL- pedestal interaction }
  under JET1 Eurofusion Work-Package. }
\cvitem{2019-20}{Scientific Coordinator of JET Experiment M18-41 
  \emph{Divertor geometry effect on detachment and SOL}
  under JET1 Eurofusion Work-Package. }
\cvitem{2019-Present}{European representative at the \emph{Pedestal
    and Edge Physics}  ITPA Topical Group}
\cvitem{2020-Present}{Deputy task force leader of EUROfusion Package
  \emph{Tokamak Exploitation}}
\cvitem{2020-Present}{Project board member of the Eurofusion E-TASC
  board under Work-package \emph{Advanced Scientific Computing}}
\end{cvblock}
