\iftoggle{nicolacv}{
\section{Education and Qualifications}
%% education for curricul a-la Friggeri
\begin{entrylist}
\entry
{1994}
{High School,  \textit{56 out 60}}
{Liceo Scientifico U.Morin,  Venezia}
{}

\entry
{1994-1999}
{Laurea in Fisica,  \\ 
M.Sc. in Physics magna cum  Laude}
{Universit\'a degli Studi di Padova}
{Thesis title: \emph{Trasporto di particelle ed energia per effetto di turbolenza
  elettrostatica in plasmi confinati in configurazione Reversed Field
  Pinch} \\
{\small\textcolor{lightgray}{Topics: Electrostatic anomalous transport. Sheared Flows.
Active modification of boundary flow through edge biasing}}}

\entry
{2000-2002}
{Ph.D in Energetics}
{Universit\'a degli Studi di Padova}
{Thesis title: \emph{Self-organization phenomena and
    coherent structure generation in magnetized plasmas} \\
{\small \textcolor{lightgray}{Topics: Electromagnetic turbulence in Reversed Field Pinches and Tokamaks.
Anomalous transport. Self Organized Criticality} }}
\end{entrylist}

}{
% alternative Curriculum vitae
\begin{cvblock}{Istruzione e formazione}
\cvitem{1993}{\textbf{Diploma di scuola superiore}, Liceo
  Scentifico Statale \emph{U.Morin},  Venezia. Voto: \textbf{56/60}}
\\[-6pt]
\cvitem{1999}{\textbf{Laurea magistrale in Fisica}, \emph{Universit{\'a} degli
  Studi di Padova}. Voto: \textbf{110/110 e lode}}
\cvitem{Titolo della tesi}{\emph{\small Trasporto di particelle ed energia per effetto
 di turbolenza elettrostatica in plasmi confinati in configurazione
 Reversed Field Pinch}}
\cvitem{Relatori}{ Prof. S. Lo Russo,  Dr. V. Antoni}
\\[-6pt]
\cvitem{2002}{\textbf{Dottorato di ricerca in Energetica}, \emph{Universit{\'a} degli
  Studi di Padova}}
\cvitem{Titolo della tesi}{\emph{\small Self-organization phenomena and
    coherent structure generation}}
\cvitem{relatori}{ Prof. A.Buffa,  Dr. V. Antoni}
\end{cvblock}
}

\iftoggle{nicolacv}{
\section{Further Education}
\begin{entrylist}
\entry
{Oct 2000}
{International School of Plasma Physics \\
and Ultrafast Optics}
{Capri,  Italy}
{}

\entry
{Sept 2001}
{5$^{th}$ Carolus Magnus Euro-Summer School \\
on Plasma and Fusion Energy Physics}
{Badhonnef,  Germany}
{}

\entry
{Jan 2002}
{International School on Topics in Nonlinear Dynamics}
{Venice,  Italy}
{}

\entry
{Jun 2011}
{5$^{th}$ International ITER Summer School on MHD  \\
and energetic
  particles}
{Aix-en-Provence, France}
{}
\end{entrylist}
}{
\begin{cvblock}{Scuole e specializzazioni}
\cvitem{2000}{\emph{International School of Plasma Physics and
    Ultrafast Optics}, Capri, Italy }
\cvitem{2001}{\emph{5$^{th}$ Carolus Magnus Euro-Summer School on
    Plasma and Fusion Energy Physics}, Badhonnef,  Germany}
\cvitem{2002}{\emph{International School on Topics in Nonlinear
    Dynamics}, Venice, Italy}
\cvitem{2011}{\emph{5$^{th}$ International Iter Summer School: MHD
    and Energetic Particles},  Aix-en-Provence, France}
\end{cvblock}
}
