\begin{cvblock}{Referenze}

\cvitem{Nome}{Prof. Volker Naulin}
\cvitem{Institute}{{\small Department of Physics, DTU Technical University of
  Denmark}}
\cvitem{}{{\small Fysikvej
Building 309, room 250
2800 Kgs. Lyngby, Denmark}}
\cvitem{email}{vona@fysik.dtu.dk} 

\\[-4pt]

\cvitem{Nome}{Prof. Ambrogio Fasoli}
\cvitem{Instituto}{{\small Swiss Plasma Center, Ecole Polytechnique Federal de
Lausanne}}
\cvitem{}{{\small EPFL SB SPC-TCV 
PPB 318 Station 13 
CH-1015 Lausanne
Switzerland}}
\cvitem{email}{ambrogio.fasoli@epfl.ch} 

\\[-4pt]

\cvitem{Nome}{Prof. James Robert Drake}
\cvitem{Instituto}{{\small Department of Fusion Plasma Physics, School of
  Electrical Engineering, Royal Institut of Technology}}
\cvitem{}{{\small Teknikringen 31, SE 100 44, Stockholm, Sweden}}
\cvitem{email}{drake@kth.se}

\\[-4pt]

\cvitem{Nome}{Prof. Francesco Gnesotto}
\cvitem{Instituto}{{\small Dipartimento di Ingegneria Industriale, Universit{\'a} degli Studi di Padova e Consorzio RFX}}
\cvitem{}{{\small Corso Stati Uniti 4,  35127 Padova, Italy}}
\cvitem{email}{francesco.gnesotto@igi.cnr.it}

\\[-4pt]

\cvitem{Nome}{Prof. Vincenzo Carbone}
\cvitem{Instituto}{{\small Dipartimento di Fisica, Universit{\'a} degli Studi
  della Calabria}}
\cvitem{}{{\small Via P. Bucci 
Arcavacata di Rende (CS), Italy}}
\cvitem{email}{vincenzo.carbone@fis.unical.it}

\\[-4pt]

\cvitem{Nome}{Prof. John S Sarff}
\cvitem{Instituto}{{\small Department of Physics, University of Winsconsin, Madison}}
\cvitem{}{{\small 1150 University Avenue Madison, WI 53706-1390}}
\cvitem{email}{jssarff@wisc.edu}

\\[-4pt]

\cvitem{Nome}{Prof. Bruce Lipschultz}
\cvitem{Instituto}{{\small Department of Physics, University of York}}
\cvitem{}{{\small Heslington York, YO10 5DD UK}}
\cvitem{email}{bruce.lipschultz@york.ac.uk}


\end{cvblock}

