\begin{cvblock}{PhD Commitee}
\cvitem{2014}{PhD Commitee at the Department of Physics, Technical
  University of Denmark. Candidate: N. Yan}

\\[-4pt]

\cvitem{2015}{PhD Commitee at the Facult{\'e} de Sciences de Base,
  Ecole Polytechnique Federale de Lausanne. Candidate:
  F. Avino. Thesis N. 6734}

\\[-4pt]

\cvitem{2016}{PhD Commitee at the Facult{\'e} de Sciences de Base,
  Ecole Polytechnique Federale de Lausanne. Candidate:
  F. Nespoli. Thesis N. 7475}

\\[-4pt]

\cvitem{2017}{PhD Commitee at the Department of Physics,
  University of York. Candidate: A. Wynn}

\\[-4pt]

\cvitem{2018}{PhD Commitee presso la Facult{\'e} de Sciences de Base,
  Ecole Polytechnique Federale de Lausanne. Candidate:
  P. Paruta. Thesis N. 8944}

\\[-4pt]

\cvitem{2018}{PhD Commitee at the Department of Physics, Technical
  University of Denmark. Candidate: J. M. Bolsen}

\\[-4pt]

\cvitem{2020}{PhD Commitee at the Facult{\'e} de Sciences de Base,
  Ecole Polytechnique Federale de Lausanne. Candidate:
  C. Beadle. Thesis N. 8279}

\\[-4pt]

\cvitem{2021}{PhD Rapporteur at the Aix-Marseille Universit{\'e}
  Candidate: R. Tatali}

\\[-4pt]

\cvitem{2022}{PhD Rapporteur at the Aix-Marseille Universit{\'e}
  Candidate: M. Scotto d'Abusco}

\end{cvblock}

\begin{cvblock}{Evaluation panel}
\cvitem{2013}{Reviewer for grant \emph{Futuro in Ricerca 2013},
    Proposal N. RBFR13MXVQ}

  \\[-4pt]

  \cvitem{2013}{Reviewer for grant \emph{PRIN 2012},
    Proposal N. 2012XAS7WZ}

  \\[-4pt]

  \cvitem{2020}{Reviewer for application to the Department of Energy,
    Office of Fusion Energy Science,  USA}

  \\[-4pt]

  \cvitem{2020}{Reviewer for application to the Czech Academy of Science}

  \\[-4pt]

  \cvitem{2020}{Reviewer for application to Sweden Research Council}

\end{cvblock}

\begin{cvblock}{Conferences Program Committee}
\cvitem{2022}{Member of the Program Committee of the 48$^{th}$ EPS Conference on Plasma Physics}

\\[-4pt]

\cvitem{2025}{Member of the Program Committee of the 2025 EU-US Transport Task Force meeting}
\end{cvblock}

% \begin{cvblock}
% \cvitem{2012}{Member of the Program committee of the \emph{17th Joint EU-US
%     Transport Task Force Meeting in combination with the 4th EFDA
%     Transport Topical Group meeting},  3-6 September 2012,  Padova
%   Italy}

% \\[-4pt]

% \cvitem{2022}{Member of the Program Committee of the \emph{48th EPS
%     Conference on Plasma Physics},  27 June - 1 July 2022,  Maastricht }
% \end{cvblock}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../cvnicola-alternative"
%%% End:
