\iftoggle{nicolacv}{
\section{Education and Qualifications}
%% education for curricul a-la Friggeri
\begin{entrylist}
\entry
{1994}
{High School,  \textit{56 out 60}}
{Liceo Scientifico U.Morin,  Venezia}
{}

\entry
{1994-1999}
{Laurea in Fisica,  \\ 
M.Sc. in Physics magna cum  Laude}
{Universit\'a degli Studi di Padova}
{Thesis title: \emph{Trasporto di particelle ed energia per effetto di turbolenza
  elettrostatica in plasmi confinati in configurazione Reversed Field
  Pinch} \\
{\small\textcolor{lightgray}{Topics: Electrostatic anomalous transport. Sheared Flows.
Active modification of boundary flow through edge biasing}}}

\entry
{2000-2002}
{Ph.D in Energetics}
{Universit\'a degli Studi di Padova}
{Thesis title: \emph{Self-organization phenomena and
    coherent structure generation in magnetized plasmas} \\
{\small \textcolor{lightgray}{Topics: Electromagnetic turbulence in Reversed Field Pinches and Tokamaks.
Anomalous transport. Self Organized Criticality} }}
\end{entrylist}

}{
% alternative Curriculum vitae
\begin{cvblock}{Education}
\cvitem{1993}{\textbf{High School Leaving Certificate}, Liceo
  Scentifico Statale \emph{U.Morin},  Venice Italy. Grade: \textbf{56/60}}
\\[-6pt]
\cvitem{1999}{\textbf{M. Sci. Physics}, \emph{Universit{\'a} degli
  Studi di Padova}. Grade: \textbf{110/100 cum Laude}}
\cvitem{Thesis Title}{\emph{\small Trasporto di particelle ed energia per effetto
 di turbolenza elettrostatica in plasmi confinati in configurazione
 Reversed Field Pinch (Particle and energy transport induced by
electrostatic turbulence in Reversed Field Pinch  plasmas)}}
\cvitem{advisor}{ Prof. S. Lo Russo,  Dr. V. Antoni}
\\[-6pt]
\cvitem{1999}{\textbf{PhD in Energetics}, \emph{Universit{\'a} degli
  Studi di Padova}}
\cvitem{Thesis Title}{\emph{\small Self-organization phenomena and
    coherent structure generation}}
\cvitem{advisor}{ Prof. A.Buffa,  Dr. V. Antoni}
\end{cvblock}


% \begin{tabular}{lll}
% March 1999 & \textbf{\textit{Laurea in Fisica} } &
% Universit\`a degli Studi di Padova, Padova, Italy \\
%  & \textbf{(M.Sci Physics)} & \textit{110 out 110 cum Laude} \\
%  &Thesis Title:  & \textbf{\emph{Trasporto di particelle ed energia per effetto
%  di turbolenza elettrostatica}} \\
% & & \textbf{\emph{in plasmi confinati in configurazione
%  Reversed Field Pinch}} \\ 
% & & (Particle and energy transport induced by
% electrostatic turbulence in \\
% & &  Reversed Field Pinch  plasmas) \\ 
% & Supervisor: & Prof. S. Lo Russo, Dr. V. Antoni \\
%  & Topics: & Electrostatic anomalous transport. Sheared Flows. \\ 
% & & Active
%  modification of boundary flow through edge biasing \\
%  March 2002 & \textbf{Ph.D in Energetics} & Universit\`a degli Studi di Padova, Padova,
% Italy \\
% & Thesis Title: & \textbf{\emph{Self-organization phenomena and
%     coherent structure generation}} \\
%  & & \textbf{\emph{in magnetized plasmas}} \\
%  & Supervisor: & Prof. A. Buffa, Dr. V. Antoni \\ 
%  & Topics: & Electromagnetic turbulence in Reversed Field Pinches and Tokamaks. \\
% & & Anomalous transport. Self Organized Criticality.
% \end{tabular}
}

\iftoggle{nicolacv}{
\section{Further Education}
\begin{entrylist}
\entry
{Oct 2000}
{International School of Plasma Physics \\
and Ultrafast Optics}
{Capri,  Italy}
{}

\entry
{Sept 2001}
{5$^{th}$ Carolus Magnus Euro-Summer School \\
on Plasma and Fusion Energy Physics}
{Badhonnef,  Germany}
{}

\entry
{Jan 2002}
{International School on Topics in Nonlinear Dynamics}
{Venice,  Italy}
{}

\entry
{Jun 2011}
{5$^{th}$ International ITER Summer School on MHD  \\
and energetic
  particles}
{Aix-en-Provence, France}
{}
\end{entrylist}
}{
\begin{cvblock}{Further Education}
\cvitem{2000}{\emph{International School of Plasma Physics and
    Ultrafast Optics}, Capri, Italy }
\cvitem{2001}{\emph{5$^{th}$ Carolus Magnus Euro-Summer School on
    Plasma and Fusion Energy Physics}, Badhonnef,  Germany}
\cvitem{2002}{\emph{International School on Topics in Nonlinear
    Dynamics}, Venice, Italy}
\cvitem{2011}{\emph{5$^{th}$ International Iter Summer School: MHD
    and Energetic Particles},  Aix-en-Provence, France}
\end{cvblock}
% \begin{tabular}{llll}
% 2000& October & \textbf{International School of Plasma Physics } &
% Capri, Italy\\
%  & &\textbf{and
%   Ultrafast Optics} & \\
% 2001& September & \textbf{5$^{th}$ Carolus Magnus Euro-Summer School on
%   Plasma } & Badhonnef, Germany \\
%  & &\textbf{and Fusion Energy Physics} & \\
% 2002& January & \textbf{International School on Topics in Nonlinear
%   Dynamics}& Venice, Italy \\
% 2011& June & \textbf{5$^{th}$ International Iter Summer School }&
% Aix-en-Provence, France \\
%   & & \textbf{MHD and Energetic Particles } & 
% \end{tabular}
}
