\iftoggle{nicolacv}{

\section{Referees}

\vspace{.1cm}

\textbf{Prof. Volker Naulin} \\
Department of Physics, Technical University of Denmark \\
Frederiksborgvej 399, Roskilde, Denmark\\
vona@fysik.dtu.dk

\vspace{.2cm}

\textbf{Prof. Ambrogio Fasoli}\\
Swiss Plasma Center \\
Ecole Polytechnique Federal de Lausanne \\
EPFL SB CRPP CRPP-TCV,  PPB 318 (Batiment PPB), Station 13, CH-1015,
Lausanne, Switzerland\\
ambrogio.fasoli@epfl.ch

\vspace{.2cm}

\textbf{Prof. Jim Drake}\\
Department of Fusion Plasma Physics, School of Electrical Engineering, Royal Institute of Technology \\
Teknikringen 31, SE 100 44 Stockholm, Sweden \\
jim.drake@ee.kth.se

\vspace{.2cm}

\textbf{Prof. Francesco Gnesotto}\\
Dipartimento di Ingegneria Industriale, Universit{\'a} degli Studi di
Padova e Consorzio RFX \\
Corso Stati Uniti 4, 3527 Padova, Italy \\
francesco.gnesotto@igi.cnr.it

\vspace{.2cm}

\textbf{Prof. Vincenzo Carbone}\\
Dipartimento di Fisica, Universit{\'a} degli Studi della Calabria \\
Via P. Bucci 
Arcavacata di Rende (CS), Italy \\
vincenzo.carbone@fis.unical.it

\vspace{.2cm}

\textbf{Prof. John S Sarff}
Department of Physics, University of Winsconsin, Madison \\
1150 University Avenue Madison, WI 53706-1390 \\
jssarff@wisc.edu

\vspace{.2cm}

\textbf{Dr. Dominique Escande}
Aix-Marseille Université, CNRS, PIIM, UMR 7345, case 321 \\
campus Saint-Jerome, FR-13013 Marseille, France \\
dominique.escande@univ-amu.fr

}{
\begin{cvblock}{Referees}

\cvitem{Name}{Prof. Volker Naulin}
\cvitem{Institute}{{\small Department of Physics, DTU Technical University of
  Denmark}}
\cvitem{}{{\small Fysikvej
Building 309, room 250
2800 Kgs. Lyngby, Denmark}}
\cvitem{email}{vona@fysik.dtu.dk} 

\\[-4pt]

\cvitem{Name}{Prof. Ambrogio Fasoli}
\cvitem{Institute}{{\small Swiss Plasma Center, Ecole Polytechnique Federal de
Lausanne}}
\cvitem{}{{\small EPFL SB SPC-TCV 
PPB 318 Station 13 
CH-1015 Lausanne
Switzerland}}
\cvitem{email}{ambrogio.fasoli@epfl.ch} 

\\[-4pt]

\cvitem{Name}{Prof. James Robert Drake}
\cvitem{Institute}{{\small Department of Fusion Plasma Physics, School of
  Electrical Engineering, Royal Institute of Technology}}
\cvitem{}{{\small Teknikringen 31, SE 100 44, Stockholm, Sweden}}
\cvitem{email}{drake@kth.se}

\\[-4pt]

\cvitem{Name}{Prof. Francesco Gnesotto}
\cvitem{Institute}{{\small Dipartimento di Ingegneria Industriale, Universit{\'a} degli Studi di Padova e Consorzio RFX}}
\cvitem{}{{\small Corso Stati Uniti 4,  35127 Padova, Italy}}
\cvitem{email}{francesco.gnesotto@igi.cnr.it}

\\[-4pt]

\cvitem{Name}{Prof. Vincenzo Carbone}
\cvitem{Institute}{{\small Dipartimento di Fisica, Universit{\'a} degli Studi
  della Calabria}}
\cvitem{}{{\small Via P. Bucci 
Arcavacata di Rende (CS), Italy}}
\cvitem{email}{vincenzo.carbone@fis.unica.it}

\\[-4pt]

\cvitem{Name}{Prof. John S Sarff}
\cvitem{Institute}{{\small Department of Physics, University of Winsconsin, Madison}}
\cvitem{}{{\small 1150 University Avenue Madison, WI 53706-1390}}
\cvitem{email}{jssarff@wisc.edu}

\\[-4pt]

\cvitem{Name}{Dr. Dominique Escande}
\cvitem{Institute}{{\small Aix-Marseille Université, CNRS, PIIM, UMR 7345}}
\cvitem{}{{\small campus Saint-Jerome, FR-13013 Marseille, France}}
\cvitem{email}{escande@ymail.com}


\end{cvblock}
}
