\begin{cvblock}{Teaching}

\cvitem{2008--2009}{Assistant for the course \emph{Fluid and Plasma
    Physics}, M.Sci degree in Physics, Department of Physics, University of Padova}

\\[-4pt]

\cvitem{2010}{Assistant for the course \emph{Fluid and Plasma
    Physics}, M.Sci degree in Physics, Department of Physics, University of Padova}

\\[-4pt]

\cvitem{2011--2012}{Assistant to the course \emph{Fundamental of
    Plasma Physics}, Bachelor degree in Physics, Department of Physics, University of Padova }

\\[-4pt]

\cvitem{2012-2013}{Assistant to the course \emph{Fundamental of
    Plasma Physics}, Bachelor degree in Physics, Department of Physics, University of Padova }

\\[-4pt]

\cvitem{2013-2014}{Assistant to the course \emph{Fundamental of
    Plasma Physics}, Bachelor degree in Physics, Department of Physics, University of Padova }

\\[-4pt]

\cvitem{2013-2014}{Lecturer for basic Physics course of the Joint Research Doctorate
and European Interuniversity Doctoral Network on Fusion Science and Engineering}

\\[-4pt]

\cvitem{2014-2015}{Assistant to the course \emph{Fundamental of
    Plasma Physics}, Department of Physics, University of Padova }

\\[-4pt]

\cvitem{2021}{Lecturer for basic \emph{Advanced Course on
    Plasma Physics and Diagnostic} per il PhD Programme in Fusion
  Science and Engineering,  Universit\`a degli Studi di Padova ed
  Universit\`a degli studi di Napoli Federico II}

\\[-4pt]

\cvitem{2023}{Lecturer for basic \emph{Advanced Course on
    Plasma Physics and Diagnostic} per il PhD Programme in Fusion
  Science and Engineering,  Universit\`a degli Studi di Padova ed
  Universit\`a degli studi di Napoli Federico II}
\end{cvblock}

\begin{cvblock}{Supervising}

\cvitem{2007}{Supervisor for Bachelor Thesis, Department of Physics,
  University of Padova, candidate: A. Scaggion}

\\[-4pt]

\cvitem{2009}{Supervisor for M.Sci. Thesis, Department of Physics,
  University of Padova, candidate: A. Scaggion}

\\[-4pt]

\cvitem{2011}{Supervisor for Bachelor Thesis, Department of Physics,
  University of Padova, candidate: A. Mazzi}

\\[-4pt]

\cvitem{2013}{Supervisor for M.Sci. Thesis, Department of Physics,
  University of Padova, candidate: A. Mazzi}

\\[-4pt]

\cvitem{2015}{Supervisor for PhD. Thesis, Department of Physics,
  University of Padova,  candidate: C. Rea}

\\[-4pt]

\cvitem{2015}{Supervisor for M.Sci. Thesis, Ecole Polytechnique
  Federale de Lausanne, candidate: M. Pedro}

\\[-4pt]

\cvitem{2020}{Supervisor for M.Sci. Thesis, Department of Physics,
  University of Padova, candidate: S. Bresciani}

\\[-4pt]

\cvitem{2019-2022}{Supervisor for PhD. Thesis in Engineering for Energy and Environment, Dipartimento di
  Ingegneria,
  Universit{\`a} della Tuscia, candidate: D. Mancini}

\\[-4pt]

\cvitem{2020-2023}{Supervisor for PhD. Thesis in Engineering for Energy and Environment, Dipartimento di
  Ingegneria,
  Universit{\`a} della Tuscia, candidate: A. Redl}

\\[-4pt]

\cvitem{2020-2023}{Supervisor for PhD. Thesis in Fusion Science and
  Engineering,
  Universit{\`a} degli Studi di Padova , candidate: A. Stagni}

\\[-4pt]
\cvitem{2022-2025}{Supervisor for PhD. Thesis in Engineering for Energy and Environment, Dipartimento di
  Ingegneria,
  Universit{\`a} della Tuscia, candidate: Y. Nakeva}

\end{cvblock}

